The results obtained in this dissertation have been published (submitted) in:
\begin{enumerate}
\item T.-T. Nguyen and C. Bonnet, ``Considerations of IP Multicast for Load Balancing in Proxy Mobile IPv6 Networks'', Accepted for publication in Computer Network, Elsevier,  Jul 2014.
\item  T.-T. Nguyen, R. Costa, and C. Bonnet, ``Experimental evaluation of wireless mo- bile networks: from methodology to a testbed”, Submitted to Wireless Networks, Springer, May 2014.
\item T.-T. Nguyen and C. Bonnet, ``On the Efficiency of Dynamic Multicast Mobility Anchor Selection in DMM: Use Cases and Analysis'', ICC, Jun 2014.
\item T.-T.  Nguyen and C. Bonnet, ``Load Balancing Mechanism for Proxy Mobile IPv6 Networks: An IP Multicast Perspective'', ICNC 2014, CNC workshop, Feb 2014. 
\item T.-T.  Nguyen, C. Bonnet, and J. Härri, ``Proxy mobile IPv6 for electric vehicle charging service: Use case and analysis'', PIMRC, Sep 2013.
\item	T.-T.  Nguyen and C. Bonnet, ``Efficient multicast content delivery over a distributed mobility management environment'', VTC2013-Fall, Sep 2013.
\item T.-T. Nguyen and C. Bonnet, ``DMM-based Inter-domain Mobility Support for Proxy Mobile IPv6'', WCNC, Apr 2013.
\item T.-T.  Nguyen and C. Bonnet, ``Performance Optimization of Multicast Content Delivery in a Mobile Environment based on PMIPv6'',  WCNC, Apr 2013.
\item	T.-T. Nguyen and Christian Bonnet, ``Optimizing Multicast Content Delivery over Novel Mobile Networks'', ICNS, Mar 2013.
\item	S. Figueiredo, C. Guimar{\~a}es, R.-L Aguiar, T.-T.  Nguyen, L. Yadin, N. Carapeto, and C. Parada,  ``Broadcasting User Content over Novel Mobile Network'', ICC, Jun 2013.
\item	S. Figueiredo, M. Wetterwald, T.-T. Nguyen, L. Eznarriaga, N. Amram, and R.-L. Aguiar, ``SVC multicast video mobility support in MEDIEVAL project'', FUTURENET 2012, Jul 2012.
%\end{itemize}
%\paragraph{Research Report}
%\begin{itemize}
\item T.-T. Nguyen, C. Bonnet, and J. Härri, ``Proxy mobile IPv6 for electric vehicle charging service: Use case and analysis'', Research Report RR-12-271, 2013.
\item T.-T. Nguyen and C. Bonnet, ``IP mobile multicast : problems and solutions'', Research report RR-11-252, 2011.
\end{enumerate}
